Paper Visualization

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
did more'

# Text preprocessing
comments_corpus <- comments_corpus %>%
  tm_map(content_transformer(tolower)) %>%  # Convert text to lowercase
  tm_map(removePunctuation) %>%              # Remove punctuation
  tm_map(removeNumbers) %>%                  # Remove numbers
  tm_map(removeWords, stopwords("english")) %>%  # Remove common stop words
  tm_map(stemDocument) %>%                   # Perform stemming
  tm_map(stripWhitespace)                    # Strip whitespace

@@

# Create the improved plot with simplified legend
co_occurrence_plot <- ggplot(graph_layout, aes(x = x, y = y)) +
  geom_edge_link(aes(edge_alpha = weight), edge_width = 0.3, color = "gray70", alpha = 0.3) +
  geom_node_point(aes(size = log1p(term_frequency[filtered_terms]), color = term_topic_df$topic_name), show.legend = TRUE, alpha = 0.8) +
  geom_text_repel(aes(label = name), 
                  max.overlaps = 20,
                  force = 10,
                  point.padding = 0.5,
                  segment.color = "gray50",
                  min.segment.length = 0,
                  box.padding = 0.7,
                  segment.size = 0.2,
                  size = 8) +
  geom_mark_hull(aes(group = term_topic_df$topic_name, fill = term_topic_df$topic_name), 
                 alpha = 0.1, show.legend = FALSE) +
  scale_size(range = c(2, 12), name = "Term Frequency") +
  scale_color_brewer(palette = "Set1", name = "Topic") +
  scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
  coord_cartesian(xlim = c(-7.5, 7.5), ylim = c(-7.5, 7.5)) +
  theme_void(base_size = 16) +
  theme(
    aspect.ratio = 1,
    legend.position = "right",
    legend.box = "vertical",
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.margin = margin(40, 40, 40, 40),
    plot.background = element_rect(fill = "white", color = NA),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  labs(title = "Co-occurrence Network of Key Themes in AIDS Discussion",
       caption = "Node size represents term frequency. Colors indicate topics identified by LDA.")

>>>>

# Text preprocessing
comments_corpus <- comments_corpus %>%
  tm_map(content_transformer(tolower)) %>%  # Convert text to lowercase
  tm_map(removePunctuation) %>%              # Remove punctuation
  tm_map(removeNumbers) %>%                  # Remove numbers
  tm_map(removeWords, stopwords("english")) %>%  # Remove common stop words
#  tm_map(stemDocument) %>%                   # Perform stemming
  tm_map(stripWhitespace)                    # Strip whitespace

@@

# Create the improved plot with simplified legend
co_occurrence_plot <- ggplot(graph_layout, aes(x = x, y = y)) +
  geom_edge_link(aes(edge_alpha = weight), edge_width = 0.3, color = "gray70", alpha = 0.3) +
  geom_node_point(aes(size = log1p(term_frequency[filtered_terms]), color = term_topic_df$topic_name), show.legend = TRUE, alpha = 0.8) +
  geom_text_repel(aes(label = name), 
                  max.overlaps = 20,
                  force = 10,
                  point.padding = 0.5,
                  segment.color = "gray50",
                  min.segment.length = 0,
                  box.padding = 0.7,
                  segment.size = 0.2,
                  size = 8) +
  geom_mark_hull(aes(group = term_topic_df$topic_name, fill = term_topic_df$topic_name), 
                 alpha = 0.1, show.legend = FALSE) +
  scale_size(range = c(2, 12), name = "Term Frequency") +
  scale_color_brewer(palette = "Set1", name = "Topic") +
  scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
  coord_cartesian(xlim = c(-8, 8), ylim = c(-8, 8)) +
  theme_void(base_size = 16) +
  theme(
    aspect.ratio = 1,
    legend.position = "right",
    legend.box = "vertical",
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.margin = margin(40, 40, 40, 40),
    plot.background = element_rect(fill = "white", color = NA),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  labs(title = "Co-occurrence Network of Key Themes in AIDS Discussion",
       caption = "Node size represents term frequency. Colors indicate topics identified by LDA.")
